### 2021-09-18 plos_latex_template.tex
RJ: Rewriting rule 1 diversity - haven't added refs yet

%   However, conferences can become discriminating spaces, in which members of some specific privileged groups reproduce the systematic inequalities that occur in academia and society \cite{arendDisparityConferenceRegistration2019, timperleyHeMoanaPukepuke2020, gewinWhatScientistsShould2019, brownAbleismAcademiaWhere2018}.

\section{Embrace all dimensions of diversity}
\label{rule_diversity}
%ast at the end i think we should go back to Embrace all dimensions of diversity
Diversity encompasses multiple dimensions: age, physical ability, career stage, gender, gender identity, geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few. Human diversity should be celebrated and respected in every way. Nonetheless, there are implicit hierarchies along these axes, and some statuses (e.g., cisgender, white, male, from the US or Europe) hold the privilege of being the default settings for which all systems --including conferences-- are consciously and unconsciously built. While no isolated initiative can change reality by itself, building a more diverse and inclusive conference starts by recognizing that these inequalities have excluded systematically whole groups of people from academia and from scientific and professional circles \cite{timperleyHeMoanaPukepuke2020}.

Depending on the field, scientific or professional communities can have very different compositions. Thinking about which subgroups have been historically excluded from your community, and thinking about which subgroups hold most privileges can help you guide the organization of a more inclusive and diverse event. Doing this exercise while you think about the reasons why you want to create a more diverse conference can prevent falling into the mistake of treating diversity as a checklist, or using diversity and inclusion work for image purposes.
%andrea: this is here because we want to avoid readers to read as recipes and treat this less seriously than how it should (and then blaming the recipe). i am not sure of the phrasing or position in the text."genuine collaborator" is in the spirit of co-liberation/co-conspirator
%Yanina: They are going to blame what they want to blame. You can't control what people are going to do and say and we shouldn't write defensively because we can't take up space in our message with that. People who do not want to change will not change because of our paper. I imagine this as a guide and help for those people who do want to do something and want to do their best and do not know what or how to do it. Or they have already done something and want to continue deepening those changes. The rest is not worth spending time and energy.  But perhaps the goals of the paper change in some other discussion and I lost that.
Actively be an ally: if you understand your own privileges (unearned advantages given by society to some people but not all) \cite{}, you can help to work on end oppression in your conference. Privilege is largely invisible to those who have it. Once we understand our own privileges, we can begin addressing them on an individual and institutional basis.
%Natalia: I'll look for a reference for privilege definition.
%marcela: I modified the paragraph a bit, but it needs more work to connect Natalia's and Andrea's ideas. It's just a suggestion, feel free to re-write it again.
%Batool: I tried making some paraphrasing - It's just a simple suggestion, not sure if it deliver the message you mean it.  I also think that we may need to define "Privilege" at the 1st mention in the 1st paragraph in this rule. Something like "Privilege is a set of unearned benefits enjoyed by a group, beyond what’s available to others."
% Rocío: The paragraph above has quite some redundancy with the paragraph below.

Think about the groups that are usually unsupported or discriminated against in your community or event, and about the meaning of "diverse" in your context. Imagine the result you would like to see if you succeeded in organizing a diverse conference according to your vision. Would this translate into an even gender distribution in your speakers? Would it be representation of all races -especially Black people-- among the head organizers, speakers, and attendees? Would it be having LGBTQIA+ friendly-spaces or community participation from key geographic regions? This is not an invitation to prioritize some dimensions of diversity above others This vision should guide and help hold the organizing team accountable along the way.

@@

%Yanina: It's probably a language problem but how I read this rule It is like to give the organizers a carte blanche to define what diversity and inclusion is and with that they are covered. What if they decide that everything is fine if they are all white people, native English speakers and without disabilities? I don't think we want to encourage that.  I mean, you need a bottom line and from them you build to improve. Plus, as it is well highligth in these rules, it is difficult to realize our own privileges, so, again, you cannot have a definition of diversity and inclusion for the conference if the team that defines it is not diverse. How are you going to have different ideas from the ones you generally have?

@@

While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. Having consideration of religious practices, setting specific accommodations for breastfeeding and child care, having LGBTQIA+-friendly spaces, creating community-only spaces, enforcing the use of pronouns, and acknowledging gender is not binary  are just some examples of decisions that can make inclusion real.
Intersectionality also needs to be taken into account, to address multiple inequalities and barriers to unprivileged people that intersect and interact with each other \cite{crenshaw1989}. Importantly, you can take active steps in creating a more welcoming environment without requiring anyone to disclose personal information.

@@

Adopting a code of conduct and creating a team to enforce it are key aspects in creating a safe environment during a conference \cite{favaroYourScienceConference2016}. The code of conduct is a document meant to keep the community safe and should state clearly: the unacceptable behaviors, the spaces of the conference in which it applies, the consequences for engaging in unacceptable behavior, and the way to report violations \cite{aurora2019}. 
The code of conduct should be displayed prominently in several spaces of the conference to deter people from unacceptable behavior, which includes microaggression .
%Rocío: Microagression. I know it's not always evident, but that's a detail I would expect in a CoC, not necessarily here unless explicitly justified.
An efficient code of conduct acts as a protection for the community because the people who are the target of unacceptable behavior tend to be the ones with less power or privilege.

@@

A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually marginalized groups (see \textbf{Rule \ref{rule_diversity}} discussing the dimensions of diversity lacking in your community and event). To ensure a deeper understanding and smooth communication with different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. If you already have an organizing team, check for biases in its composition.

@@

Creating and maintaining such a team and space may seem more challenging than working in homogeneous teams, but the positive outcomes far outweigh any inconveniences. 
Having diverse people in decision-making positions will affect positively all the other aspects of your conference because all the processes will benefit from their input, expertise, and distinct perspectives \cite{hongGroupsDiverseProblem2004}. In addition, a diverse team plays an important role at creating a welcoming space because seeing people with similar life experiences occupy public spaces, positions of power, and breaking negative stereotypes (i.e., representation) matters (see Rule \ref{rule_inclusion}). This is specially important for networking spaces, where receiving ideas, direct feedback, and spaces to co-lead from a wide variety of community members can be the key to organize meaningful sessions for all the conferences attendees. This gave a sense of variety and an appeal of “at least one networking session for everyone”. %Rocío: this networking part could go in a box.

%Representation is an important aspect of diversity and inclusion: seeing people like you, from your country, that speak your language is one of the best way to feel you belong

Most advice when working with a diverse team should apply to every team, but is especially true when working with people from marginalized groups. First, delegate. Don't expect self-nomination and voting to work as mechanisms to counteract systemic inequalities. Nominate directly and offer coordinating positions, even if this means stepping down. Offer mentorship and guidance if you encounter cases of impostor syndrome, doubts about the use of English in communication (See Rule \ref{rule_language}), or others. You can, for example, break the expectations about leadership as a lonely task and create smaller, co-led groups, where everyone finds their preferred tasks and gets to take leadership. Splitting the workload and responsibilities should not be done by putting care-taking labors --community building, meeting organization and note taking, conversations with potential partners-- on the hands of women and other minoritized groups, while people from privileged groups take the lead in stereotypical highly-valued tasks (see Rule \ref{rule_spotlight}).

Set the tone. %adding here from Liz's rule but maybe this could go in communication in general
In addition to excluding derogatory or discriminatory language (remember that the code of conduct applies to you too, Rule \ref{rule_inclusion}), make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being defensive.

@@

\section{Consciously unbias your spotlight roles}
\label{rule_spotlight}

@@

Make sure that every selection committee --the committee looking for keynote speakers, the selection committee for abstracts, the prizes and award committees --are also diverse \cite{swartzScienceValueDiversity2019, wongBuildDiversityScience2020}, and ask them to be aware that everyone has an implicit biases, to recognize them, and try to counteract them.  An inclusive and diverse organizing team (\textbf{Rule \ref{rule_organizing_team}}) is already a great starting point to overcome this bias in other roles. The regional and local communities in your field are also good sources to tap into. 
For example, for useR! 2021, groups like AfricaR (africa-r.org), R-Ladies (rladies.org), MiR (mircommunity.com), Forwards (forwards.github.io), and LatinR (latin-r.com) were fundamental to reach people for the organizing team, potential presenters, to co-lead social events, and attendees; some of them even held spaces to help the members of their groups to prepare abstracts for submission.
When organizing an international academic conference, you may reach local associations, student organizations or other Early Career Researchers groups or communities of practice: ask their needs and barriers, and explicitly invite them to contribute to the conference. Since many conferences are held with the primary goal of displaying cutting-edge work led by senior scientists and academics, early career researchers are often disadvantaged. Diversity should spread among all speaking roles, and the conference should also help raise the profiles of early career researchers, fostering collaboration and building their skills.

Furthermore, consider bringing to the spotlight the people that have contributed to your field in more collaborative  ways \cite{cheng2020x+}. Give awards (see Rule \ref{rule_accessibility}) to those who prepared accessible slides and presentations, for instance, to acknowledge being mindful of inclusiveness. Community building, for instance, is challenging and usually unrewarded when compared to publications or software development \cite{acionWhyChooseCommunity2020}; give the people who deliberately took the time to work on their communities the recognition they deserve. Defy the stereotypical criteria for success by acknowledging these community practices. 
However, do not restrict people from marginalized groups or community-builders to talk or work only in issues related to Diversity, Inclusion, and Accessibility. Recognize their areas of expertise and respect their will regarding participation (or not) in community-building events.

@@

Take advantage of the online setting for new networking activities that can be inclusive for people with different socialization styles and accessibility needs. Social events in in-person conferences are often the most exclusive, and they are a very common place where you have code of conduct violations.
% Rocío: I think that we should justify why we say that "social events in in-person conferences are often the most exclusive"
Having them directly translated into their virtual versions does not address the need for creating opportunities for people to meet and bond. An online event is a great opportunity to create spaces for people who do not enjoy in person networking. Some ideas in this line are: offering the option of written chat only, instead of voice or video conversations, opening events with team work like trivia, offer some events that can be passively enjoyed like movies, yoga sessions, or art displays, where attendants can choose to just sit and enjoy without talking, or have a chat channel to comment on their experiences during the session. Respect people’s limits, preferences, and remember that “the usual” does not necessarily work with your community, and that one single networking activity will never serve the whole community. It is worth trying new and varied activities that might work with subgroups of attendees.

@@

\section{Express this welcoming spirit in your communication strategy}
\label{rule_communication}
%Andrea: this rule name should be more explicit towards communication, "promoting"
\begin{itemize}
    \item Promotion: Actively reach out and promote the conference to people who have been systematically excluded/Outreach/promotion plan that reaches communities that are traditionally excluded in scientific meetings
    \item Express this welcoming spirit in your communication strategy: Be public about your commitment to equity and inclusion: display the CoC prominently in conference spaces, publish the diversity statement, fee waivers, abstract selection process
    \item Languages
    \item Words matter: Be careful how you talk about minoritized people, Assertively set tone of inclusion
\end{itemize}

@@

\section{Set fair registration rates and provide financial support when needed}
\label{rule_costs}

% Rocío: Rewrite as a design rule.

Conferences, even virtual ones, should have registration fees for two primary reasons. The first one is that preparing the conference involves a lot of concerted effort and costs money (e.g., commercial registration tools, captioning, or conference venue, if in-person) and this translates to the participation fee. The second reason has to do with psychology -- people value more the things they pay for, and there is a lower attendance rate for free events than for events with registration costs \cite{eventbrite_ultimate_2017}.

@@

Offering scholarships or grants to attend the conference may be counterproductive, as they can be seen as more of a competition and attract people that might not need the money (e.g., when their PI could pay for it) but could apply for it to enrich their CV while filtering out people who do not feel entitled to earn them. If the goal is to help the people who really need it, the language needs to make that clear without shrouding it with fancy-sounding phrases or terms that single out the recipients (e.g. `grant recipient' or `diversity scholar', respectively). Do not call it a scholarship or a grant. Ultimately, it is a fee waiver or a discount for the people who need additional financial support. Also, the process for applicants should be simplified. Applying for loans, grants, and scholarships may be an emotionally demanding task. Do not complicate the attendees' lives by asking for long essays to convince a committee that they deserve your support. For this stage of the process, a certain degree of trust goes a long way -- when they say they need the support, it is best to give them the waiver rather than second guess their eligibility. If the conference resources allow for it, you could even take further steps to offer financial support for activities that help them have the time and resources to be at the conference: child care support, transportation fees and visa financial and administrative support (if in-person), or internet connection services (if virtual). If the conference is virtual, you may offer technical support so that attendees can record their videos, include captions, or design accessible presentations.

>>>>

% keeping references:
%   However, conferences can become discriminating spaces, in which members of some specific privileged groups reproduce the systematic inequalities that occur in academia and society \cite{arendDisparityConferenceRegistration2019, timperleyHeMoanaPukepuke2020, gewinWhatScientistsShould2019, brownAbleismAcademiaWhere2018}.

\section{Embrace all dimensions of diversity}
\label{rule_diversity}

Diversity encompasses multiple dimensions: age, physical ability, career stage, gender, gender identity, geographic origin, language, neurodiversity, race, religion, sexual orientation, and socioeconomic background, to name a few. 
Human diversity should be celebrated and respected in every way. Nonetheless, we live in a world with implicit hierarchies along these axes, and some statuses (e.g., cisgender, white, male, from the US or Europe) hold the privilege of being the default settings for which all systems--including conferences--are consciously and unconsciously built.  
%sara: reference for privilege: McIntosh, Peggy. "White privilege: Unpacking the invisible knapsack." (1988).
While no isolated initiative can change reality by itself, building a more diverse and inclusive conference starts by recognizing that these inequalities have excluded systematically whole groups of people from academia and from scientific and professional circles \cite{timperleyHeMoanaPukepuke2020}.

To be proactive allies in our conferences and communities, we should start by examining our own privileges (unearned advantages given by society to some people but not all).
Privilege is largely invisible to those who have it. And we will not be able to help end discrimination and oppression if we do not recognize our privileges first and the injustices that come with them.
Once we understand our own privileges, we can begin addressing them on an individual, collective, and institutional basis.
Recognizing our privileges--particularly in our field and in our scientific or professional community--will help identify which subgroups have been the most excluded or discriminated against. 
These are the groups we need to make more effort to include. 
Depending on the field, region or community, it could be Black, LGBTQIA+, Muslim, or others. 
Intersectionality, or the complex, cumulative way in which the effects of multiple forms of discrimination combine or intersect, should be taken into account.

Investing more in effort in the most excluded groups does not mean neglecting the others (see Rule 2 for more on that). 
But it will prevent from falling into the mistake of treating diversity as a checklist.
It will also guide the vision of diversity for your conference--and your strategies to achieve it:
Will a more diverse conference would translate into an even gender distribution in your speakers? 
Would it be representation of all races--especially Black people--among the head organizers, speakers, and attendees? 
Would it be having LGBTQIA+ friendly-spaces or community participation from key geographic regions?
This exercise will also help coming up with indicators that would help the organizing team assess the fulfillment of the diversity objectives along the way. 
%sara: reference for privilege: McIntosh, Peggy. "White privilege: Unpacking the invisible knapsack." (1988).

@@

@@

While it is essential to improve representation towards some of the most visible dimensions of human diversity, such as race, gender, and country of origin, building a truly inclusive environment means taking care of all the other aspects of diversity as well. Having consideration of religious practices, setting specific accommodations for breastfeeding and child care, having LGBTQIA+-friendly spaces, creating community-only spaces, enforcing the use of pronouns, and acknowledging gender is not binary are just some examples of decisions that can make inclusion real.
Intersectionality also needs to be taken into account, to address multiple inequalities and barriers to unprivileged people that intersect and interact with each other \cite{crenshaw1989}. 
%sara: i'd move the intersectionality phrase to the last paragraph of the first rule, right before 'This vision should guide and help hold the organizing team accountable along the way.' Here, I'd just write: 
Importantly, you can take active steps in creating a more welcoming environment without requiring anyone to disclose personal information.

@@

%i took the networking part to expand communication att.ast we can switch back afterwards

Adopting a code of conduct and creating a team to enforce it are key aspects in creating a safe environment during a conference \cite{favaroYourScienceConference2016}. The code of conduct is a document meant to keep the community safe and should state clearly: the unacceptable behaviors, the spaces of the conference in which it applies, the consequences for engaging in unacceptable behavior, and the way to report violations \cite{aurora2019}. 
The code of conduct should be displayed prominently in several spaces of the conference to deter people from unacceptable behavior.
%Rocío: Microagression. I know it's not always evident, but that's a detail I would expect in a CoC, not necessarily here unless explicitly justified.
An efficient code of conduct acts as a protection for the community because the people who are the target of unacceptable behavior tend to be the ones with less power or privilege.

@@

A genuinely inclusive conference can only be organized by an inclusive and diverse organizing team. Build a team with people from different regions, genders, socioeconomic statuses, and other aspects of diversity. Particular attention should be paid to the usually marginalized groups (see \textbf{Rule \ref{rule_diversity}}) discussing the dimensions of diversity lacking in your community and event. To ensure a deeper understanding and smooth communication with different diverse groups, it is essential to create a representative working group that functions as a snapshot of the community at large. If you already have an organizing team, check for biases in its composition.

@@

Creating and maintaining such a team and space may seem more challenging than working in homogeneous teams, but the positive outcomes far outweigh any inconveniences. %sara: inconveniences here doesn't sound good. I'd use: the positive outcomes are worth it
Having diverse people in decision-making positions will affect positively all the other aspects of your conference because all the processes will benefit from their input, expertise, and distinct perspectives \cite{hongGroupsDiverseProblem2004}. In addition, a diverse team plays an important role at creating a welcoming space because representation -seeing people with similar life experiences occupy public spaces, positions of power, and breaking negative stereotypes- is one of the best ways to create a sense of belonging (see Rule \ref{rule_inclusion}). This is specially important for networking spaces, where receiving ideas, direct feedback, and spaces to co-lead from a wide variety of community members can be the key to organize meaningful sessions for all the conferences attendees. This gave a sense of variety and an appeal of “at least one networking session for everyone”. 
%ast 17sep: i think we can talk here about planning neworking here, but also: the whole paragraph applies to team dynamics in general. Sara: maybe you can use this as we spoke relating team work here. And I think the working together part is not here but the following paragraph 
%sara: The last sentence in the paragraph sounds odd to me, but maybe I'm missing something. Andrea, I added a few sentences to the following paragraph regarding work dynamics

Most advice when working with a diverse team should apply to every team, but is especially true when working with people from marginalized groups. First, rethink power relationships inside the group and share power. Be committed to examine power relations inside your organizing team and challenge it during all the process.
Don't expect self-nomination and voting to work as mechanisms to counteract systemic inequalities. Nominate directly and offer coordinating positions, and let people from privileged groups step down. 
Build an environment in which every person has their voice and enforce voices from systematically excluded groups.
Offer mentorship and guidance if you encounter cases of impostor syndrome, doubts about the use of English in communication (See Rule \ref{rule_language}), or others. You can, for example, break the expectations about leadership as a lonely task and create smaller, co-led groups, where everyone finds their preferred tasks and gets to take leadership. Splitting the workload and responsibilities should not be done by putting care-taking labors --community building, meeting organization and note taking, conversations with potential partners-- on the hands of women and other minoritized groups, while people from privileged groups take the lead in stereotypical highly-valued tasks (see Rule \ref{rule_spotlight}). Make work visible, discuss collectively what should be done (and why), divide and account work. Being transparent and sharing the information is key to make work visible and collective. %sara: this relates to make labor visible from DF, maybe we can cite them here too.

%sara: agree that this fits better in the communication rule
Set the tone. %adding here from Liz's rule but maybe this could go in communication in general
In addition to excluding derogatory or discriminatory language, make the effort to teach yourself the vocabulary and the best ways to communicate to account for every culture and situation. Do not expect people to teach you --it's not their role-- and accept feedback without being defensive.

@@

\section{Consciously unbias your spotlight roles}
\label{rule_spotlight}%sara: rule_unbias?

@@

Make sure that every selection committee --the committee looking for keynote speakers, the selection committee for abstracts, the prizes and award committees --are also diverse \cite{swartzScienceValueDiversity2019, wongBuildDiversityScience2020}, and ask them to be aware that everyone has implicit biases, to recognize them, and try to counteract them. 
An inclusive and diverse organizing team (\textbf{Rule \ref{rule_organizing_team}}) is already a great starting point to overcome this bias in other roles. The regional and local communities in your field are also good sources to tap into. 
For example, for useR! 2021, groups like AfricaR (africa-r.org), R-Ladies (rladies.org), MiR (mircommunity.com), Forwards (forwards.github.io), and LatinR (latin-r.com) were fundamental to reach people for the organizing team, potential presenters, to co-lead social events, and attendees; some of them even held spaces to help the members of their groups to prepare abstracts for submission.
When organizing an international academic conference, you may reach local associations, student organizations or other Early Career Researchers groups or communities of practice: ask for their requirements and barriers, and explicitly invite them to contribute to the conference. Since many conferences are held with the primary goal of displaying cutting-edge work led by senior scientists and academics, early career researchers are often disadvantaged. Diversity should spread among all speaking roles, and the conference should also help raise the profiles of early career researchers, fostering collaboration and building their skills.

Furthermore, consider bringing to the spotlight the people that have contributed to your field in more collaborative ways \cite{cheng2020x+}. You can, for instance, reframe the awards ceremony to acknowledge those who prepared accessible slides and presentations (see Rule \ref{rule_accessibility}), to acknowledge being mindful of inclusiveness. Community building, for instance, is challenging and usually unrewarded when compared to publications or software development \cite{acionWhyChooseCommunity2020}; give the people who deliberately took the time to work on their communities the recognition they deserve. Defy the stereotypical criteria for success by acknowledging these community practices. 
Finally, do not restrict people from marginalized groups or community-builders to talk or work only in issues related to Diversity, Inclusion, and Accessibility. Recognize their areas of expertise and respect their will regarding participation (or not) in community-building events.

@@

Take advantage of the online setting for new networking activities that can be inclusive for people with different socialization styles and accessibility needs. Social events in in-person conferences are often the most exclusive (i.e., galas, dinner nights at expensive venues), and they are a very common place where you have code of conduct violations.
% Rocío: I think that we should justify why we say that "social events in in-person conferences are often the most exclusive"
%ast: exclusionary? i added a couple of examples

Having them directly translated into their virtual versions does not address the need for creating opportunities for people to meet and bond. An online event is a great opportunity to create spaces for people who do not enjoy in person networking. Some ideas in this line are: offering the option of written chat only, instead of voice or video conversations, opening events with team work like trivia, offer some events that can be passively enjoyed like movies, yoga sessions, or art displays, where attendants can choose to just sit and enjoy without talking, or have a chat channel to comment on their experiences during the session. Respect people’s limits, preferences, and remember that “the usual” does not necessarily work with your community, and that one single networking activity will never serve the whole community. It is worth trying new and varied activities that might work with subgroups of attendees.

@@

\section{Express this welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words.

\begin{itemize}
    \item Promotion: Actively reach out and promote the conference to people who have been systematically excluded/Outreach/promotion plan that reaches communities that are traditionally excluded in scientific meetings
    \item Express this welcoming spirit in your communication strategy: Be public about your commitment to equity and inclusion: display the CoC prominently in conference spaces, publish the diversity statement, fee waivers, abstract selection process
    \item Languages
    \item Words matter: Be careful how you talk about minoritized people, Assertively set tone of inclusion
    \item coherence between actions and words
    \item \textbf{networking} when you gather a diverse groups of attendants you also have to take care of the spaces where they will interact
\end{itemize}

@@

\section{Allocate financial resources to support the presence of diverse people in every space of the conference
}
\label{rule_financial}
%ast: new overall rationale (feel free to comment and change): conferences are expensive to organize and some work on limited budgets. this repercutes in fee costs -but fees for attendance are exclusionary- there should be fees, less no-shows. fees should be set fairly. 
%scholarships or grants to attend are a common way to boost participation from diverse groups but they attract people who believe they'll win -already privileged- people who do not need them but could use the prestige (for lack of another word) to fit in their cv, 
% Rocío: Rewrite as a design rule.
\subsection{Set fair registration rates and provide financial support when needed}
Conferences, even virtual ones, should have registration fees for two primary reasons. The first one is that preparing the conference involves a lot of concerted effort and costs money (e.g., commercial registration tools, captioning, or conference venue, if in-person) and this translates to the participation fee. The second reason has to do with psychology -- people value more the things they pay for, and there is a lower attendance rate for free events than for events with registration costs \cite{eventbrite_ultimate_2017}.

@@

Offering scholarships or grants to attend the conference are a common way to boost participation from diverse groups, and some conferences ask for cover letters or applications  but they may be counterproductive, as they can be seen as more of a competition and attract people that might not need the money (e.g., when their PI could pay for it) but could apply for it to enrich their CV while filtering out people who do not feel entitled to earn them. If the goal is to help the people who really need it, the language needs to make that clear without shrouding it with fancy-sounding phrases or terms that single out the recipients (e.g. `grant recipient' or `diversity scholar', respectively). Do not call it a scholarship or a grant. Ultimately, it is a fee waiver or a discount for the people who need additional financial support. Also, the process for applicants should be simplified. Applying for loans, grants, and scholarships may be an emotionally demanding task. Do not complicate the attendees' lives by asking for long essays to convince a committee that they deserve your support. For this stage of the process, a certain degree of trust goes a long way -- when they say they need the support, it is best to give them the waiver rather than second guess their eligibility.

If the conference resources allow for it, you could even take further steps to offer financial support for activities that help them have the time and resources to be at the conference: child care support, transportation fees and visa financial and administrative support (if in-person), or internet connection services (if virtual). If the conference is virtual, you may offer technical support so that attendees can record their videos, include captions, or design accessible presentations.
